---
title: "Image Selection for DSR"
author: "Rayus Kuplicki, Laureate Institute for Brain Research"
date: "Feb 10, 2020"
output: 
  html_document:
    code_folding: hide
    highlight: tango
    theme: cerulean
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
word_document: default

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
```
```{r set-options, echo=FALSE, cache=FALSE}
options(width = 300)
```


## IAPS Stress image selection

```{r}

set.seed(12345)
#columns to match between opioid, neutral, and IAPS stress images for different sets of images
#allsubjects_arousal_mean
#allsubjects_valence_mean

#hue_mean
#saturation_mean
#value_mean

#allsubjects_craving_mean

#IAPS stress images Rajita's group used--will keep these 66, and add 30 more for a total of 96
images_rajita <- read.table('images-yale.tsv', header = TRUE)
images_rajita <- images_rajita[images_rajita$PicNum != 'grayfix',]
length(unique(images_rajita$PicNum))
rajita_ids <- unique(images_rajita$PicNum)

dir.create('IAPS-Rajita')
#put files Rajita used in a folder for easy viewing
for (id in rajita_ids){
  file.copy(paste0('../media/IAPS20081_20/IAPS1_20Images/', id, '.jpg'), 'IAPS-Rajita')
}

data_iaps <- read.table('AllSubjects_1-20.txt', header = TRUE)
library(ggplot2)
data_iaps$rajita_used <- data_iaps$IAPS %in% rajita_ids
library(stringr)
hsv_iaps <- read.csv('HSV-IAPS.csv')
hsv_iaps$IAPS <- str_replace(hsv_iaps$File, '.jpg', '')
#add hue/saturation/value into data_iaps
data_iaps <- merge(data_iaps, hsv_iaps)
#select 30 more IAPS images with valence < 3 and arousal > 4

data_iaps$possible_option <- !data_iaps$rajita_used & (data_iaps$valmn < 3) & (data_iaps$aromn > 4)
#list of possible new images to select

#remove drug/alcohol related IAPS (beer bottle, cigarette butts, drug injection)
data_iaps$possible_option[data_iaps$IAPS %in% c(2710, 9830, 2751, 2717, 2750, 9007)] <- FALSE

possible_idxs <- (1:nrow(data_iaps))[data_iaps$possible_option]
#pick 30 of them at random
new_iaps <- sample(possible_idxs, 30)
data_iaps$selection_group <- 'Unused'
data_iaps$selection_group[data_iaps$rajita_used] <- 'RajitaUsed'
data_iaps$selection_group[new_iaps] <- 'NewlySelected'

dir.create('IAPS-new')
#put files Rajita used in a folder for easy viewing
for (id in data_iaps[data_iaps$selection_group == 'NewlySelected', 'IAPS']){
  file.copy(paste0('../media/IAPS20081_20/IAPS1_20Images/', id, '.jpg'), 'IAPS-new')
}

#show valence/arousal of all IAPS, images rajita used, and newly selected images
ggplot(data = data_iaps) + geom_point(aes(x = valmn, y = aromn, color = selection_group)) + ggtitle('IAPS Images Used')
library(tableone)
print("Comparing Rajita's IAPS stress images to our newly selected ones:")
CreateTableOne(data = data_iaps[data_iaps$selection_group != 'Unused',], vars = c('valmn', 'aromn', 'hue_mean', 'saturation_mean', 'value_mean'), strata = 'selection_group')

#grab just the selected IAPS images, then split them randomly into the 4 image sets
selected_data_iaps <- data_iaps[data_iaps$selection_group != 'Unused',]
selected_data_iaps$in_set <- sample(rep(1:4, 24))

names(selected_data_iaps)[names(selected_data_iaps) == 'valmn'] <- 'allsubjects_valence_mean'
names(selected_data_iaps)[names(selected_data_iaps) == 'aromn'] <- 'allsubjects_arousal_mean'
selected_data_iaps$ImageSet <- 'stress'


```



  
  


## Neutral and Opioid image selection

```{r}


data_mocd <- read.csv('DCR_summaries_7-3-2019.csv')
#ggplot(data = data_mocd) + geom_point(aes(x = allsubjects_valence_mean, y = allsubjects_arousal_mean, color = ImageSet))

#ggplot(data = data_mocd[data_mocd$ImageSet != 'meth',]) + geom_histogram(aes(x = allsubjects_craving_mean, color = ImageSet, fill = ImageSet))

selection_data <- data_mocd

#remove opioid image 118 because 109 and 118 are the same 
selection_data <- selection_data[(selection_data$Group != 'opioid Slide118.jpeg'),]

#remove images with text on them
selection_data <- selection_data[!(selection_data$Group %in%  c('opioid Slide015.jpeg', 'opioid Slide016.jpeg', 'opioid Slide017.jpeg', 
                                                                'opioid Slide018.jpeg', 'opioid Slide019.jpeg', 'opioid Slide020.jpeg',
                                                                'control Slide017.jpeg', 'control Slide018.jpeg', 'control Slide019.jpeg', 'control Slide020.jpeg')),]

#remove light bulb images, since they can be associated with drug use
selection_data <- selection_data[!(selection_data$Group %in%  c('control Slide057.jpeg', 'control Slide087.jpeg')),]

#get rid of meth images
selection_data <- selection_data[selection_data$ImageSet != 'meth',]

#remove image set averages (e.g. mean opioid_hand etc.)
selection_data <- selection_data[!is.na(selection_data$File),]


#select images based on distance to a target HSV
try_one_criteria <- function(control_target_hue, control_target_saturation, control_target_value,
                             opioid_target_hue, opioid_target_saturation, opioid_target_value){
  #sorted_data <- selection_data[sample(nrow(selection_data)),]
  
  selection_data$selection_cost <- NA
  selection_data$selection_cost[selection_data$ImageSet == 'control'] <- 
    (selection_data$hue_mean[selection_data$ImageSet == 'control'] - control_target_hue)^2 + 
    (selection_data$saturation_mean[selection_data$ImageSet == 'control'] - control_target_saturation)^2 +
    (selection_data$value_mean[selection_data$ImageSet == 'control'] - control_target_value)^2
  
  
  selection_data$selection_cost[selection_data$ImageSet == 'opioid'] <- 
    (selection_data$hue_mean[selection_data$ImageSet == 'opioid'] - opioid_target_hue)^2 + 
    (selection_data$saturation_mean[selection_data$ImageSet == 'opioid'] - opioid_target_saturation)^2 +
    (selection_data$value_mean[selection_data$ImageSet == 'opioid'] - opioid_target_value)^2
  
  
  (selection_data$hue_mean - 0.3)^2 + (selection_data$saturation_mean - 0.3)^2 + (selection_data$value_mean - 0.3)^2
  #this line to select based on high/low craving rating
  #sorted_data <- selection_data[order(selection_data$allsubjects_craving_mean),]
  #this line to select based on HSV cost
  sorted_data <- selection_data[order(selection_data$selection_cost),]


  
  #label categories 1:6, to make indexing into number_selected easier
  
  sorted_data$category_number <- NA
  
  sorted_data$category_number[sorted_data$Category == 'control_objects'] <- 1
  sorted_data$category_number[sorted_data$Category == 'control_objects_hand'] <- 2
  sorted_data$category_number[sorted_data$Category == 'control_tool'] <- 3
  sorted_data$category_number[sorted_data$Category == 'control_tool_hand_simple'] <- 4
  sorted_data$category_number[sorted_data$Category == 'control_tool_hand_complex'] <- 5
  sorted_data$category_number[sorted_data$Category == 'control_tool_face'] <- 6
  
  
  sorted_data$category_number[sorted_data$Category == 'opioid'] <- 1
  sorted_data$category_number[sorted_data$Category == 'opioid_hand'] <- 2
  sorted_data$category_number[sorted_data$Category == 'opioid_injection_instrument'] <- 3
  sorted_data$category_number[sorted_data$Category == 'opioid_instrument_hand'] <- 4
  sorted_data$category_number[sorted_data$Category == 'opioid_injection_hand'] <- 5
  sorted_data$category_number[sorted_data$Category == 'opioid_face_activities'] <- 6
  
  #number in each group that have been selected 
  number_selected <- c(0, 0, 0, 0, 0, 0)
  
  #go forward, marking the first 12 in each category of control images for selection
  #will set to TRUE for images selected to be used
  sorted_data$selected <- FALSE
  
  
  for (i in 1:nrow(sorted_data)){
    #step forwards, taking the least craving-iducing neutral images
    if (sorted_data$ImageSet[i] != 'control') {
      next
    }
    this_category <- sorted_data$category_number[i]
    if (number_selected[this_category] > 15){
      next
    }
    number_selected[this_category] <- number_selected[this_category] + 1
    sorted_data[i, 'selected'] <- TRUE
  }
  #some categories have < 16 items, so fill out 96 images from categories that have more
  for (i in 1:nrow(sorted_data)){
    #step forwards, taking the least craving-iducing neutral images
    if (sorted_data$ImageSet[i] != 'control' | sorted_data[i, 'selected']) {
      next
    }
    
    this_category <- sorted_data$category_number[i]
    if (number_selected[this_category] > 18){
      next
    }
    number_selected[this_category] <- number_selected[this_category] + 1
    sorted_data[i, 'selected'] <- TRUE
    if (sum(number_selected) == 96){
      break
    }
  } 
  
  
  #number in each group that have been selected 
  number_selected_opioid <- c(0, 0, 0, 0, 0, 0)
  #step through backwards, selecting most craving-inducing meth/opioid images
  #for (i in nrow(sorted_data):1){
  for (i in 1:nrow(sorted_data)){  
    
    this_category <- sorted_data$category_number[i]
    this_group <- sorted_data$ImageSet[i]
    if (this_group == 'opioid'){
      if (number_selected_opioid[this_category] > 15){
        next
      }
      number_selected_opioid[this_category] <- number_selected_opioid[this_category] + 1
      sorted_data[i, 'selected'] <- TRUE
    }
  }
  #some categories have < 16 items, so fill out 96 images from categories that have more
  for (i in 1:nrow(sorted_data)){
    #step forwards, taking the least craving-iducing neutral images
    if (sorted_data$ImageSet[i] != 'opioid' | sorted_data[i, 'selected']) {
      next
    }
    
    this_category <- sorted_data$category_number[i]
    if (number_selected_opioid[this_category] > 19){
      next
    }
    number_selected_opioid[this_category] <- number_selected_opioid[this_category] + 1
    sorted_data[i, 'selected'] <- TRUE
    if (sum(number_selected_opioid) == 96){
      break
    }
  } 
  
  selected_data <- sorted_data[sorted_data$selected,]
  
  
  selected_data$in_set <- NA
  #will randomize these
  in_set <- c(1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4)
  
  #some categories have 16 or fewer, assign those first and keep a list of image sets with fewer than expected due to < 16 in some categories
  extras_control <- c()
  for (i in 1:6){
    number_inset <- length(selected_data[selected_data$category_number == i & selected_data$ImageSet == 'control', 'in_set'])
    if (number_inset < 17){
      random_order <- in_set[sample(16)]
      selected_data[selected_data$category_number == i & selected_data$ImageSet == 'control', 'in_set'] <- random_order[1:number_inset]
      if(number_inset < 16){
        extras_control <- c(extras_control, random_order[(number_inset + 1):16])
      }
    }
  }
  #now, for those categories that had > 16 images, pass them out to the image sets in extras_control
  for (i in 1:6){
    number_inset <- length(selected_data[selected_data$category_number == i & selected_data$ImageSet == 'control', 'in_set'])
    if (number_inset > 16){
      this_inset <- c(in_set, extras_control[1:(number_inset - 16)])
      extras_control <- extras_control[(number_inset - 15):length(extras_control)]
      random_order <- this_inset[sample(number_inset)]
      selected_data[selected_data$category_number == i & selected_data$ImageSet == 'control', 'in_set'] <- random_order
    }
  }
  
  #some categories have 16 or fewer, assign those first and keep a list of image sets with fewer than expected due to < 16 in some categories
  extras_opioid <- c()
  for (i in 1:6){
    number_inset <- length(selected_data[selected_data$category_number == i & selected_data$ImageSet == 'opioid', 'in_set'])
    if (number_inset < 17){
      random_order <- in_set[sample(16)]
      selected_data[selected_data$category_number == i & selected_data$ImageSet == 'opioid', 'in_set'] <- random_order[1:number_inset]
      if(number_inset < 16){
        extras_opioid <- c(extras_opioid, random_order[(number_inset + 1):16])
      }
    }
  }
  #now, for those categories that had > 16 images, pass them out to the image sets in extras_opioid
  for (i in 1:6){
    number_inset <- length(selected_data[selected_data$category_number == i & selected_data$ImageSet == 'opioid', 'in_set'])
    if (number_inset > 16){
      this_inset <- c(in_set, extras_opioid[1:(number_inset - 16)])
      extras_opioid <- extras_opioid[(number_inset - 15):length(extras_opioid)]
      random_order <- this_inset[sample(number_inset)]
      selected_data[selected_data$category_number == i & selected_data$ImageSet == 'opioid', 'in_set'] <- random_order
    }
  }
  
  
  
  #selected_data[selected_data$category_number == i & selected_data$ImageSet == 'opioid', 'in_set'] <- in_set[sample(16)]
  
  library(tableone)
  
  allsets_tab <- CreateTableOne(vars = c('allsubjects_arousal_mean', 'allsubjects_craving_mean', 'allsubjects_typicality_mean', 'allsubjects_valence_mean', 
                                         'hue_mean', 'saturation_mean', 'value_mean'),
                                strata = c('ImageSet'), data = selected_data)
  print(allsets_tab)
  
  
  return(selected_data)
}
#instead, let's select based on hue and see if that helps balance things--get images closest to 0.2
#try_one_criteria <- function(control_target_hue, control_target_saturation, control_target_value,
#                             meth_target_hue, meth_target_saturation, meth_target_value,
#                             opioid_target_hue, opioid_target_saturation, opioid_target_value){


```

## Select Opioid and Control images

```{r}
selected_data <- try_one_criteria(0.4, 1, 0.5,
                 0.2, 0.8, 0.5)

library(data.table)

combined <- rbindlist(list(selected_data, selected_data_iaps), fill = TRUE, use.names = TRUE)
combined <- as.data.frame(combined)
#combine selected IAPS data with opioid/control data, so we can summarize all data sets

#get all neutral images not selected, so we can use them to make a practice schedule
neutral_remaining <- selection_data[selection_data$ImageSet == 'control' & !(selection_data$Group %in% combined$Group),]

```

## Control/Stress/Opioid overall comparison

```{r}
set_tab <- CreateTableOne(vars = c('allsubjects_arousal_mean', 'allsubjects_craving_mean', 'allsubjects_typicality_mean', 'allsubjects_valence_mean', 
                                       'hue_mean', 'saturation_mean', 'value_mean'),
                      strata = c('ImageSet'), data = combined)
print(set_tab)

```



## Control/Stress/Opioid Set 1

```{r}

set1_tab <- CreateTableOne(vars = c('allsubjects_arousal_mean', 'allsubjects_craving_mean', 'allsubjects_typicality_mean', 'allsubjects_valence_mean', 
                                       'hue_mean', 'saturation_mean', 'value_mean'),
                      strata = c('ImageSet'), data = combined[combined$in_set == 1,])
print(set1_tab)

```

## Control/Stress/Opioid Set 2

```{r}

set2_tab <- CreateTableOne(vars = c('allsubjects_arousal_mean', 'allsubjects_craving_mean', 'allsubjects_typicality_mean', 'allsubjects_valence_mean', 
                                       'hue_mean', 'saturation_mean', 'value_mean'),
                      strata = c('ImageSet'), data = combined[combined$in_set == 2,])
print(set2_tab)

```

## Control/Stress/Opioid Set 3

```{r}

set3_tab <- CreateTableOne(vars = c('allsubjects_arousal_mean', 'allsubjects_craving_mean', 'allsubjects_typicality_mean', 'allsubjects_valence_mean', 
                                       'hue_mean', 'saturation_mean', 'value_mean'),
                      strata = c('ImageSet'), data = combined[combined$in_set == 3,])
print(set3_tab)

```
## Control/Stress/Opioid Set 4

```{r}

set4_tab <- CreateTableOne(vars = c('allsubjects_arousal_mean', 'allsubjects_craving_mean', 'allsubjects_typicality_mean', 'allsubjects_valence_mean', 
                                       'hue_mean', 'saturation_mean', 'value_mean'),
                      strata = c('ImageSet'), data = combined[combined$in_set == 4,])
print(set4_tab)

```


## Control images compared across session

```{r}
control_tab <- CreateTableOne(vars = c('allsubjects_arousal_mean', 'allsubjects_craving_mean', 'allsubjects_typicality_mean', 'allsubjects_valence_mean', 
                                       'hue_mean', 'saturation_mean', 'value_mean'),
                      strata = c('in_set'), data = combined[combined$ImageSet == 'control',])
control_tab


```

## Opioid images compared across session

```{r}
opioid_tab <- CreateTableOne(vars = c('allsubjects_arousal_mean', 'allsubjects_craving_mean', 'allsubjects_typicality_mean', 'allsubjects_valence_mean', 
                                      'hue_mean', 'saturation_mean', 'value_mean'),
                           strata = c('in_set'), data = combined[combined$ImageSet == 'opioid',])
opioid_tab

```

## Stress images compared across session

```{r}

stress_tab <- CreateTableOne(vars = c('allsubjects_arousal_mean', 'allsubjects_craving_mean', 'allsubjects_typicality_mean', 'allsubjects_valence_mean', 
                                      'hue_mean', 'saturation_mean', 'value_mean'),
                           strata = c('in_set'), data = combined[combined$ImageSet == 'stress',])
stress_tab


```





## Write output


```{r}
#IAPS images have no categories (hands, tools, etc) so set category_number to 0 for them
combined$category_number[is.na(combined$category_number)] <- 0
write.csv(combined, 'DSR_selected_split.csv', row.names=FALSE, quote = FALSE)


#For convenient viewing, copy images to subfolders for session and category
for(imset in 1:4){
  dir.create(paste0('set-', imset))
  for (category in unique(combined$ImageSet)){
    #opioid/control/stress
    dir.create(paste0('set-', imset, '/', category))
  }
}



neutral_path = '../media/MethOpioidDatabase/finalcueset/ExtractedNeutralCues120/'
stress_path = '../media/IAPS20081_20/IAPS1_20Images/'
opioid_path = '../media/MethOpioidDatabase/finalcueset/ExtractedOpioidCues120/'

for (i in 1:nrow(combined)){
  this_file <- combined$File[i]
  this_category <- combined$ImageSet[i]
  this_set <- combined$in_set[i]
  if (this_category == 'stress'){
    this_path <- stress_path
  }
  if (this_category == 'control'){
    this_path <- neutral_path
  }
  if (this_category == 'opioid'){
    this_path <- opioid_path
  }
  print(i)
  print('copy from:')
  print(paste0(this_path, this_file))
  print('copy to:')
  print(paste0('set-', this_set, '/', this_category))
  file.copy(paste0(this_path, this_file), paste0('set-', this_set, '/', this_category))
}


  



```




## Generate schedules based on selected split

```{r}

neutral_path = 'media\\MethOpioidDatabase\\finalcueset\\ExtractedNeutralCues120\\'
stress_path = 'media\\IAPS20081_20\\IAPS1_20Images\\'
opioid_path = 'media\\MethOpioidDatabase\\finalcueset\\ExtractedOpioidCues120\\'


#study-PASO_condition-stress_set-1
#make a schedule based on one condition and set

generate_schedules_one_condition <- function(condition, condition_numeric, category_path, condition_name){
  #condition_name so 'control' schedules can be output with 'neutral'n in the name
  #condition <- 'control'
  #condition_numeric <- '1'
  #category_path <- neutral_path
  for (image_set in 1:4){
    #image_set <- 1
  
    #extract the 24 images for this condition/set
    these_images <- combined[combined$ImageSet == condition & combined$in_set == image_set,]
    #will have 6 ITI fixations total, average of 10s
    fixations <- sample(c(8,8,10,12,12))
    #idx of next fixation to use
    fix_idx = 1
    #sort by category
    these_images <- these_images[order(these_images$category_number),]
    #now assign blocks
    these_images$block <- rep(1:4, 6)
    output_text <- 'TrialTypes,Stimuli,Durations,ExtraArgs \n'
    output_text <- paste0(output_text, '000,media\\fixation.png,31,\n')
    output_text <- paste0(output_text, '100,media\\valence.png,5,\n')
    output_text <- paste0(output_text, '200,media\\arousal.png,5,\n')
    output_text <- paste0(output_text, '300,media\\stress.png,5,\n')
    output_text <- paste0(output_text, '400,media\\craving.png,5,\n')
   
    
    output_text <- paste0(output_text, '000,media\\fixation.png,31,\n')
    output_text <- paste0(output_text, '100,media\\valence.png,5,\n')
    output_text <- paste0(output_text, '200,media\\arousal.png,5,\n')
    output_text <- paste0(output_text, '300,media\\stress.png,5,\n')
    output_text <- paste0(output_text, '400,media\\craving.png,5,\n')
    
    #fixation after ratings, since we don't want to jump straight into images
    output_text <- paste0(output_text, '000,media\\fixation.png,', fixations[fix_idx], ',\n')
    fix_idx = fix_idx + 1
      
    for (block in 1:4){
      #grab images for this block
      this_block <- these_images[these_images$block == block,]
      #shuffle the images in this block
      this_block <- this_block[sample(6),]
      #which image will have a box around it
      this_box <- sample(6, 1)
      for(i in 1:6){
        this_category <- this_block$category_number[i]
        this_image_path <- paste0(category_path, this_block$File[i])
        if (i == this_box){
          this_trial_type <- paste0('8', condition_numeric, this_category)
        } else{
          this_trial_type <- paste0('0', condition_numeric, this_category)
        }
        output_text <- paste0(output_text, this_trial_type, ',', this_image_path, ',5,\n')
      }
      #ratings
      output_text <- paste0(output_text, '1', condition_numeric, '0,media\\valence.png,5,\n')
      output_text <- paste0(output_text, '2', condition_numeric, '0,media\\arousal.png,5,\n')
      output_text <- paste0(output_text, '3', condition_numeric, '0,media\\stress.png,5,\n')
      output_text <- paste0(output_text, '4', condition_numeric, '0,media\\craving.png,5,\n')
      if (block < 4){
        #no fixation after the last block, because the next trial is a long fixation--so the cross doesn't flash in the middle
        output_text <- paste0(output_text, '000,media\\fixation.png,', fixations[fix_idx], ',\n')
        fix_idx = fix_idx + 1
      }
    }
    
    output_text <- paste0(output_text, '000,media\\fixation.png,31,\n')
    output_text <- paste0(output_text, '100,media\\valence.png,5,\n')
    output_text <- paste0(output_text, '200,media\\arousal.png,5,\n')
    output_text <- paste0(output_text, '300,media\\stress.png,5,\n')
    output_text <- paste0(output_text, '400,media\\craving.png,5,\n')
    output_text <- paste0(output_text, '000,media\\fixation.png,', fixations[fix_idx], ',\n')
    fix_idx = fix_idx + 1
    #here, there will still be a 200ms blip, right as the audio starts--so that's probably OK
    output_text <- paste0(output_text, '999,media\\fixation.png,360,\n')
  
  
    cat(output_text, file = paste0('study-PASO_task-DSR_condition-', condition_name, '_set-', image_set, '.schedule'))
  }
}

generate_schedules_one_condition('control', '1', neutral_path, 'neutral')
generate_schedules_one_condition('opioid', '2', opioid_path, 'opioid')
generate_schedules_one_condition('stress', '3', stress_path, 'stress')

```

##Write practice schedule

```{r}

#one block of fixation, ratings, one block of images, ratings, then relaxation audio

#right now (a la table(neutral_remaining$Catgory)) we have:
#16 control_tool
#1 control_tool_face
#1 control_tool_hand_simple
#so we don't have all tools, use the control_tool_face, control_tool_hand_simple images, and 3 control_tool images
#

#set category_number, for practice trial types
neutral_remaining$category_number <- NA
  
neutral_remaining$category_number[neutral_remaining$Category == 'control_objects'] <- 1
neutral_remaining$category_number[neutral_remaining$Category == 'control_objects_hand'] <- 2
neutral_remaining$category_number[neutral_remaining$Category == 'control_tool'] <- 3
neutral_remaining$category_number[neutral_remaining$Category == 'control_tool_hand_simple'] <- 4
neutral_remaining$category_number[neutral_remaining$Category == 'control_tool_hand_complex'] <- 5
neutral_remaining$category_number[neutral_remaining$Category == 'control_tool_face'] <- 6

control_tool_idx <- (1:nrow(neutral_remaining))[neutral_remaining$Category == 'control_tool']
control_tool_idx_selected <- sample(control_tool_idx,4)
these_images <- neutral_remaining[control_tool_idx_selected,]

#add in hte one control_tool_face image
these_images <- rbind(these_images, neutral_remaining[neutral_remaining$Category == 'control_tool_face',])
these_images <- rbind(these_images, neutral_remaining[neutral_remaining$Category == 'control_tool_hand_simple',])

#now assign blocks
output_text <- 'TrialTypes,Stimuli,Durations,ExtraArgs \n'
output_text <- paste0(output_text, '000,media\\fixation.png,31,\n')
output_text <- paste0(output_text, '100,media\\valence.png,5,\n')
output_text <- paste0(output_text, '200,media\\arousal.png,5,\n')
output_text <- paste0(output_text, '300,media\\stress.png,5,\n')
output_text <- paste0(output_text, '400,media\\craving.png,5,\n')
   
output_text <- paste0(output_text, '000,media\\fixation.png,8,\n')

#fixation after ratings, since we don't want to jump straight into images

#shuffle the images in this block
these_images <- these_images[sample(6),]
#which image will have a box around it
this_box <- sample(6, 1)
condition_numeric <- '1'
for(i in 1:6){
  this_category <- these_images$category_number[i]
  this_image_path <- paste0(neutral_path, these_images$File[i])
  if (i == this_box){
    this_trial_type <- paste0('8', condition_numeric, this_category)
  } else{
    this_trial_type <- paste0('0', condition_numeric, this_category)
  }
  output_text <- paste0(output_text, this_trial_type, ',', this_image_path, ',5,\n')
}
#ratings
output_text <- paste0(output_text, '110,media\\valence.png,5,\n')
output_text <- paste0(output_text, '210,media\\arousal.png,5,\n')
output_text <- paste0(output_text, '310,media\\stress.png,5,\n')
output_text <- paste0(output_text, '410,media\\craving.png,5,\n')
output_text <- paste0(output_text, '000,media\\fixation.png,8,\n')

output_text <- paste0(output_text, '999,media\\fixation.png,140,\n')
  
  
cat(output_text, file = paste0('study-PASO_task-DSR_condition-neutral_set-P.schedule'))


```

































